Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-05-08 paper.tex
Mark all edits as permanent.

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{nicefrac}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
%\usepackage{url}
%\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}

\usepackage[normalem]{ulem}

@@

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh (\texttt{vpraveen@cmu.edu}) %(\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
		and Pulkit Grover (\texttt{pulkit@cmu.edu}) %(\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
	}
	\IEEEauthorblockA{
		Electrical \& Computer Engineering,
		and the Center for the Neural Basis of Cognition,
		Carnegie Mellon University
		%\\
		%\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
		%\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	}
	\thanks{
	\textcolor{red}{The full version of this paper is available online~\cite{FullVersion}.}

	This work was supported in part by NSF CNS-1702694 and by Systems on
	Nanoscale Information fabriCs (SONIC), one of the six SRC STARnet Centers,
	sponsored by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by
	the Dowd Fellowship from the College of Engineering at Carnegie Mellon
	University.  The authors would like to thank Philip and Marsha Dowd for
	their financial support and encouragement. The authors thank Prof.\ Anand
	Sarwate and Prof.\ Aarti Singh for their useful comments.
	}
	\vspace{-0.25in}
}

@@

\textcolor{red}{
\sout{Recent developments} Our recent work~\cite{Grover2016Information}
\sout{have suggested} suggests that source localization can benefit greatly
from an increase in sensor density. \sout{This conclusion is based primarily on
	a Nyquist rate analysis} Revisiting the Nyquist rate arguments presented
in~\cite{Nunez2006Electric} revealed that the question of how source imaging
resolution is affected by sensor density has not been addressed. We argued
intuitively that under appropriate conditions the right algorithms might be
able to recover the brain signal with much higher fidelity if more sensors were
used. To follow up on these intuitive arguments, Grover provides an
information-theoretic bound~\cite{Grover2016Fundamental} on the accuracy of
source localization algorithms.} This information-theoretic bound, however, was
derived for the unsampled, continuous-space potential on the scalp, or
equivalently, in the limit of the number of sensors going to infinity. \textcolor{red}{\sout{The
claim that source localization can benefit from increased sensor density is,
therefore, not fully substantiated by the information-theoretic bound, since it
does not provide a lower bound that shows improvement with increasing sensor
density.} Hence, this bound does not substantiate the claim that source
localization can benefit from increased sensor density.}

@@

This paper seeks to address the shortcomings of earlier methods by deriving
lower bounds on the minimax risk for the source localization problem, which
apply to \emph{all} estimators (biased \emph{and} unbiased), and which capture
how the bound scales with increasing numbers of sensors. Previous lower bounds
are based on ``spherical head
models''~\cite{Nunez2006Electric,Grover2016Information}, which admit analytical
solutions for the potential of a single dipole. But spherical models are not
easily amenable to analytical lower bounds which seek to capture scaling in the
number of sensors, because the spherical surface does not permit uniform
sampling~\cite{Heath1956Thirteen}. We therefore restrict our analysis to a
source localization problem on a one-dimensional ``circular'' domain (to be
described in detail in Section~\ref{sec:source-localization}). \textcolor{red}{While this
simplified model makes crucial assumptions (such as shift-invariance) that do
not hold in realistic brain models, the techniques presented here extend
naturally for deriving numerical bounds in more complex settings.}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{array}
\usepackage{enumitem}
\usepackage{color}
%\usepackage{url}
%\usepackage[colorlinks=true,allcolors=black,urlcolor=blue]{hyperref}

%\usepackage[normalem]{ulem}

@@

\author{
	\IEEEauthorblockN{
		Praveen Venkatesh (\texttt{vpraveen@cmu.edu}) %(\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}) %\IEEEauthorrefmark{1}
		and Pulkit Grover (\texttt{pulkit@cmu.edu}) %(\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}) %\IEEEauthorrefmark{2}
	}
	\IEEEauthorblockA{
		Electrical \& Computer Engineering,
		and the Center for the Neural Basis of Cognition,
		Carnegie Mellon University
		%\\
		%\IEEEauthorrefmark{1}\href{mailto:vpraveen@cmu.edu}{\texttt{vpraveen@cmu.edu}}
		%\IEEEauthorrefmark{2}\href{mailto:pulkit@cmu.edu}{\texttt{pulkit@cmu.edu}}
	}
	\thanks{
	The full version of this paper is available online~\cite{FullVersion}.

	This work was supported in part by NSF CNS-1702694 and by Systems on
	Nanoscale Information fabriCs (SONIC), one of the six SRC STARnet Centers,
	sponsored by MARCO and DARPA.  Praveen Venkatesh was supported (in part) by
	the Dowd Fellowship from the College of Engineering at Carnegie Mellon
	University.  The authors would like to thank Philip and Marsha Dowd for
	their financial support and encouragement. The authors thank Prof.\ Anand
	Sarwate and Prof.\ Aarti Singh for their useful comments.
	}
	%\vspace{-0.25in}
}

@@

Our recent work~\cite{Grover2016Information} suggests that source localization
can benefit greatly from an increase in sensor density. Revisiting the Nyquist
rate arguments presented in~\cite{Nunez2006Electric} revealed that the question
of how source imaging resolution is affected by sensor density has not been
addressed. We argued intuitively that under appropriate conditions, the right
algorithms might be able to recover the brain signal with much higher fidelity
if more sensors were used. To follow up on these intuitive arguments, Grover
provides an information-theoretic bound~\cite{Grover2016Fundamental} on the
accuracy of source localization algorithms. This information-theoretic bound,
however, was derived for the unsampled, continuous-space potential on the
scalp, or equivalently, in the limit of the number of sensors going to
infinity. Hence, this bound does not substantiate the claim that source
localization can benefit from increased sensor density.

@@

This paper seeks to address the shortcomings of earlier methods by deriving
lower bounds on the minimax risk for the source localization problem, which
apply to \emph{all} estimators (biased \emph{and} unbiased), and which capture
how the bound scales with increasing numbers of sensors. Previous lower bounds
are based on ``spherical head
models''~\cite{Nunez2006Electric,Grover2016Information}, which admit analytical
solutions for the potential of a single dipole. But spherical models are not
easily amenable to analytical lower bounds which seek to capture scaling in the
number of sensors, because the spherical surface does not permit uniform
sampling~\cite{Heath1956Thirteen}. We therefore restrict our analysis to a
source localization problem on a one-dimensional ``circular'' domain (to be
described in detail in Section~\ref{sec:source-localization}). While this
simplified model makes crucial assumptions (such as shift-invariance) that do
not hold in realistic brain models, the techniques presented here extend
naturally for deriving numerical bounds in more complex settings.
